ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating section 2 and references
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\textcolor{blue}{ESBMC-GPU is built on top of ESBMC}, which is an open source context-bounded model checker based on SMT solvers for ANSI-C/C$++$ programs~\cite{cordeiro:2011,cordeiro:2012}, and adds four essential models, as described below.

@@

@@

\bibitem{ramalho:2013}
Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L., and Fischer, B.
\newblock {\em{SMT-Based Bounded Model Checking of C++ Programs}}.
\newblock {{ECBS}} 2013; 147--156.

>>>>

\textcolor{blue}{ESBMC-GPU is built on top of ESBMC}, which is an open source context-bounded model checker based on SMT solvers for \textcolor{blue}{ANSI-C/C$++$ programs~\cite{cordeiro:2011, cordeiro:2012, ramalho:2013}}, and adds four essential models, as described below.

@@

\bibitem{ramalho:2013}
\textcolor{blue}{Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L., and Fischer, B.}
\newblock \textcolor{blue}{{\em{SMT-Based Bounded Model Checking of C++ Programs}}.}
\newblock \textcolor{blue}{Proceedings of the $20^{th}$ Annual IEEE International Conference and Workshops on the Engineering of Computer Based Systems, ECBS'13.}
\newblock \textcolor{blue}{{IEEE} Computer Society: Washington, DC, USA, 147--156, 2013.}

@@

%\bibitem{ramalho:2013}
%Ramalho, M., Freitas, M., Sousa, F., Marques, H., Cordeiro, L., and Fischer, B.
%\newblock {\em{SMT-Based Bounded Model Checking of C++ Programs}}.
%\newblock {{ECBS}} 2013; 147--156.
